---
title: "Finding Home in France: A Data-Driven Approach to City Selection"
subtitle: "HarvardX PH125.9x Data Science Capstone - Choose Your Own Project"
author: "Adam Solomon"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6
)

# Load required libraries
library(tidyverse)
library(knitr)
library(scales)
```

# Executive Summary

[TODO: Write after analysis is complete. Include key findings, methodology overview, and main conclusions in 1-2 paragraphs.]

# Introduction

## Dataset Description

This project analyzes French real estate transaction data from the DVF (Demandes de Valeurs Foncières) database, a comprehensive open dataset published by the French government. The DVF dataset contains all property sales in France from 2020 to 2025, including transaction prices, property characteristics, and geographic information.

Supplementary datasets include:

- **Communes master file**: Geographic and administrative data for all French municipalities
- **INSEE population data**: Demographic structure by age brackets at the commune level
- **Météo France climate normals**: Sunshine hours, temperature, and rainfall data for major cities

## Project Goal

The goal of this project is to develop a data-driven methodology for identifying optimal cities for relocation in France, based on a combination of climate preferences, demographic characteristics, and real estate market conditions. The analysis will culminate in predictive models for property values and a ranked list of recommended cities.

## Personal Motivation

[TODO: Add personal context for why this analysis matters to you.]

# Methods & Analysis

## Data Sources

The analysis draws on multiple data sources:

1. **DVF (Demandes de Valeurs Foncières)**: French government open data on property transactions
   - Years covered: 2020-2025
   - Source: data.gouv.fr

2. **Communes Reference Data**: INSEE administrative boundaries and postal codes
   - Source: data.gouv.fr

3. **Population by Age**: INSEE census data with 10 age brackets
   - Source: data.gouv.fr (INSEE RP 2020)

4. **Climate Data**: Météo France 30-year climate normals
   - Variables: sunshine hours, temperature, rainfall

```{r data-sources, eval=FALSE}
# Data loading code will be sourced from scripts/cyo_project.R
source("../scripts/cyo_project.R")
```

## City Selection Criteria

To identify candidate cities for relocation, I filtered France's major metropolitan areas using three criteria: climate (annual sunshine hours), demographics (population age structure), and real estate market dynamics. The following visualizations illustrate why [FINAL CITIES] emerged as top candidates.

### Climate Screening

[TODO: Visualizations of sunshine hours, temperature comparisons]

### Demographic Screening

[TODO: Population age structure analysis, dependency ratios]

### Real Estate Market Screening

[TODO: Price trends, transaction volumes, market liquidity]

## Data Preparation

### Data Cleaning

[TODO: Describe data cleaning steps, handling missing values, outlier treatment]

### Feature Engineering

[TODO: Describe derived variables, transformations]

### Final Dataset Structure

[TODO: Summary statistics of the analysis-ready dataset]

## Modeling Approach

### Model Selection

[TODO: Describe models considered and rationale for selection]

### Training and Validation

[TODO: Describe cross-validation strategy, train/test split]

### Evaluation Metrics

[TODO: Define RMSE, R-squared, and other metrics used]

# Results

## Exploratory Data Analysis

[TODO: Key visualizations and insights from EDA]

## Model Performance

[TODO: Model comparison table, performance metrics]

## City Rankings

[TODO: Final ranked list with supporting visualizations]

# Conclusion

## Summary of Findings

[TODO: Recap of main findings and recommendations]

## Limitations

[TODO: Discuss data limitations, methodological constraints]

## Future Work

[TODO: Potential extensions and improvements]

# References

- DVF Open Data: https://www.data.gouv.fr/fr/datasets/demandes-de-valeurs-foncieres/
- INSEE Population Data: https://www.insee.fr/
- Météo France Climate Normals: https://meteofrance.com/
- R Core Team (2024). R: A language and environment for statistical computing.
- Wickham H, et al. (2019). Welcome to the tidyverse. Journal of Open Source Software.

# Appendix

## Session Info

```{r session-info}
sessionInfo()
```
